---
title: "2019 Philippine General Election Plots"
author: |
  | [curiositybits.cc](curiositybits.cc)

date: "Updated on `r Sys.Date()`"
output: 
 html_document:
   toc: yes
   code_folding: show
   highlight: haddock
   theme: lumen
   toc_float: yes
---
```{r setup, include=FALSE}
library(ggplot2) 
library(prettydoc)
library(ggthemes)

load(file = "plot.rda")

```

## Tweet volume

```{r echo=FALSE, message=FALSE, warning=FALSE}
title <- paste0("Tweet volume as of ", Sys.Date())

ggplot(data = bycandidate_pc, aes(x = reorder(from_user_screen_name, value), y = value)) +
  geom_bar(aes(fill = variable), stat = "identity") + 
  #geom_text(aes(label=round(avg_rt, digits = 2)))+
  xlab("Candidates") + ylab("Tweet volume") +
  coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  geom_smooth(method = "lm", se = FALSE) +
  scale_fill_discrete(name = "Tweet type", labels=c("tweet_count"="original tweets", "totaltweetscount_sinceoct2018"="retweets of other users"))+
  #scale_color_fivethirtyeight("cyl") +
  theme_fivethirtyeight()+theme(legend.position = "bottom")+ggtitle(title)
```

## # of hashtags 

The figure below shows the total number of hashtags used in candidates' _original_ tweets.


```{r echo=FALSE, message=FALSE, warning=FALSE}
title <- paste0("Hashtag count as of ", Sys.Date())

ggplot(data = bycandidate, aes(x = reorder(from_user_screen_name, hashtagcount), y = hashtagcount)) +
  geom_bar(aes(fill = from_user_screen_name), stat = "identity") + 
  #geom_text(aes(label=round(avg_rt, digits = 2)))+
  xlab("Candidates") + ylab("Hashtag Count") +
  coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_fivethirtyeight()+theme(legend.position = "none")+ggtitle(title)

```

## # of Twitter mentions 

The figure below shows the total number of users mentioned in candidates' _original_ tweets.

```{r echo=FALSE, message=FALSE, warning=FALSE}
title <- paste0("Mention count as of ", Sys.Date())

ggplot(data = bycandidate, aes(x = reorder(from_user_screen_name, mentioncount), y = mentioncount)) +
  geom_bar(aes(fill = from_user_screen_name), stat = "identity") + 
  #geom_text(aes(label=round(avg_rt, digits = 2)))+
  xlab("Candidates") + ylab("Mention Count") +
  coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_fivethirtyeight()+theme(legend.position = "none")+ggtitle(title)

```

## # of images/videos

The figure below shows the total number of images/videos used in candidates' _original_ tweets.

```{r echo=FALSE, message=FALSE, warning=FALSE}
title <- paste0("Image/video count as of ", Sys.Date())

ggplot(data = bycandidate, aes(x = reorder(from_user_screen_name, multimediacount), y = multimediacount)) +
  geom_bar(aes(fill = from_user_screen_name), stat = "identity") + 
  #geom_text(aes(label=round(avg_rt, digits = 2)))+
  xlab("Candidates") + ylab("Media Count") +
  coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_fivethirtyeight()+theme(legend.position = "none")+ggtitle(title)

```

## Retweet Count

The figure below shows the average number of times candidates' _original_ tweets are retweeted.

```{r echo=FALSE, message=FALSE, warning=FALSE}
title <- paste0("Average retweet count as of ", Sys.Date())

ggplot(data = bycandidate, aes(x = reorder(from_user_screen_name, avg_rt), y = avg_rt)) +
  geom_bar(aes(fill = from_user_screen_name), stat = "identity") + 
  #geom_text(aes(label=round(avg_rt, digits = 2)))+
  xlab("Candidates") + ylab("Average Retweet Count") +
  coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_fivethirtyeight()+theme(legend.position = "none")+ggtitle(title)

```

## Average Favorite Count

The figure below shows the average number of times candidates' _original_ tweets are favorited.

```{r echo=FALSE, message=FALSE, warning=FALSE}

title <- paste0("Average favorite count as of ", Sys.Date())

ggplot(data = bycandidate, aes(x = reorder(from_user_screen_name, avg_fav), y = avg_fav)) +
  geom_bar(aes(fill = from_user_screen_name), stat = "identity") + 
  #geom_text(aes(label=round(avg_rt, digits = 2)))+
  xlab("Candidates") + ylab("Average Favorite Count") +
  coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_fivethirtyeight()+theme(legend.position = "none")+ggtitle(title)

```

## Follower count

The figure below shows the number of followers each candidate has.

```{r echo=FALSE, message=FALSE, warning=FALSE}
title <- paste0("Follower count as of ", Sys.Date())

ggplot(data = bycandidate, aes(x = reorder(from_user_screen_name, followercount), y = followercount)) +
  geom_bar(aes(fill = from_user_screen_name), stat = "identity") + 
  #geom_text(aes(label=round(avg_rt, digits = 2)))+
  xlab("Candidates") + ylab("Follower Count") +
  coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_fivethirtyeight()+theme(legend.position = "none")+ggtitle(title)

```

## Friend count

The figure below shows the number of users a candidate is following on Twitterh.

```{r echo=FALSE, message=FALSE, warning=FALSE}
title <- paste0("Friend count as of ", Sys.Date())

ggplot(data = bycandidate, aes(x = reorder(from_user_screen_name, friendcount), y = friendcount)) +
  geom_bar(aes(fill = from_user_screen_name), stat = "identity") + 
  #geom_text(aes(label=round(avg_rt, digits = 2)))+
  xlab("Candidates") + ylab("Friend Count") +
  coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_fivethirtyeight()+theme(legend.position = "none")+ggtitle(title)

```



